Large-scale harmonic patterns clustering

### 2010-02-25 Paper/Paper.tex
putting pieces together

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}

% Title.
% ------
\title{PAPER TEMPLATE FOR ISMIR 2010}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
The abstract should be placed at the top left column and should contain about 150-200 words.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\section{Page Size}\label{sec:page_size}

The proceedings will be printed on 
 \underline{portrait A4-size paper} \underline{(21.0cm x 29.7cm)}. 
All material on each page should fit within a rectangle of 17.2cm x 25.2cm, 
centered on the page, beginning 2.0cm 
from the top of the page and ending with 2.5cm from the bottom. 
The left and right margins should be 1.9cm. 
The text should be in two 8.2cm columns with a 0.8cm gutter. 
All text must be in a two-column format. 
Text must be fully justified.

\section{Typeset Text}\label{sec:typeset_text}

\subsection{Normal or Body Text}\label{subsec:body}

Please use a 10pt (point) Times font. Sans-serif or non-proportional fonts 
can be used only for special purposes, such as distinguishing source code text.

The first paragraph in each section should not be indented, but all other paragraphs should be.

\subsection{Title and Authors}

The title is 14pt Times, bold, caps, upper case, centered.
Authors' names are omitted when submitting for double-blind reviewing. 
The following is for making a camera-ready version. 
Authors' names are centered. 
The lead author's name is to be listed first (left-most), and the co-authors' names after. 
If the addresses for all authors are the same, include the address only once, centered. 
If the authors have different addresses, put the addresses, evenly spaced, under each authors' name.

\subsection{First Page Copyright Notice}

Please include the copyright notice exactly as it appears here in the lower left-hand corner of the page. 
It is set in 8pt Times.

\subsection{Page Numbering, Headers and Footers}

Do not include headers, footers or page numbers in your submission. 
These will be added when the publications are assembled.

\section{First Level Headings}

First level headings are in Times 10pt bold, 
centered with 1 line of space above the section head, and 1/2 space below it. 
For a section header immediately followed by a subsection header, the space should be merged.

\subsection{Second Level Headings}

Second level headings are in Times 10pt bold, flush left, 
with 1 line of space above the section head, and 1/2 space below it. 
The first letter of each significant word is capitalized.

\subsubsection{Third and Further Level Headings}

Third level headings are in Times 10pt italic, flush left, 
with 1/2 line of space above the section head, and 1/2 space below it. 
The first letter of each significant word is capitalized.

Using more than three levels of headings is highly discouraged.

\section{Footnotes and Figures}

\subsection{Footnotes}

Indicate footnotes with a number in the text.\footnote{This is a footnote.} 
Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear. 
Precede the footnote with a 0.5pt horizontal rule.

\subsection{Figures, Tables and Captions}

All artwork must be centered, neat, clean, and legible. 
All lines should be very dark for purposes of reproduction and art work should not be hand-drawn. 
The proceedings are not in color, and therefore all figures must make sense in black-and-white form. 
Figure and table numbers and captions always appear below the figure. 
Leave 1 line space between the figure or table and the caption. 
Each figure or table is numbered consecutively. Captions should be Times 10pt. 
Place tables/figures in text as close to the reference as possible. 
References to tables and figures should be capitalized, for example: 
see \figref{fig:example} and \tabref{tab:example}. 
Figures and tables may extend across both columns to a maximum width of 17.2cm.

\begin{table}
 \begin{center}
 \begin{tabular}{|l|l|}
  \hline
  String value & Numeric value \\
  \hline
  Hello ISMIR  & 2010 \\
  \hline
 \end{tabular}
\end{center}
 \caption{Table captions should be placed below the table.}
 \label{tab:example}
\end{table}

\begin{figure}
 \centerline{\framebox{
 \includegraphics[width=\columnwidth]{figure.png}}}
 \caption{Figure captions should be placed below the figure.}
 \label{fig:example}
\end{figure}

\section{Equations}

Equations should be placed on separated lines and numbered.
The number should be on the right side, in parentheses.

\begin{equation}
E=mc^{2}
\end{equation}

\section{Citations}

All bibliographical references should be listed at the end, 
inside a section named ``REFERENCES,'' numbered and in alphabetical order. 
Also, all references listed should be cited in the text. 
When referring to a document, type the numbering square brackets
\cite{Author:00} or \cite{Author:00,Someone:10,Someone:04}.

\begin{thebibliography}{citations}

\bibitem {Author:00} 
E. Author:
``The Title of the Conference Paper,''
{\it Proceedings of the International Symposium 
on Music Information Retrieval}, pp.~000--111, 2000.

\bibitem{Someone:10} 
A. Someone, B. Someone, and C. Someone:
``The Title of the Journal Paper,''
{\it Journal of New Music Research}, 
Vol.~A, No.~B, pp.~111--222, 2010.

\bibitem{Someone:04} 
X. Someone and Y. Someone:
{\it Title of the Book},
Editorial Acme, Utrecht, 2004.

\end{thebibliography}

%\bibliography{ismir2010template}

>>>>

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}

% Title.
% ------
\title{Large-scale harmonic patterns clustering}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
We present a method for discovering typical patterns in music.
Similar to the \textit{shingle} idea, but done on a larger scale through
Echo Nest API, we cluster harmonic patterns from 43K songs. Patterns are
made of ordered chroma features, and not of summarization like gaussian
mixtures coefficients or NMF weights. We explain
how to operate on such large datasets, we analyze the obained clusters,
and we discuss there use for retrieval and encoding. All code is made
available.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\section{Previous Work}\label{sec:prevwork}
The idea is closely related to the \textit{Shingles} described by
Slaney and Casey \cite{Casey2006,Casey2007,Casey2008}. LSH: \cite{E2LSH}.
Barrington et al. recently studied music texture using a set of ordered
chroma vectors \cite{Barrington2009a}. 
Nearest neighbor for music also includes \cite{Cano2004} and ...

\section{Data}\label{sec:data}

\subsection{Echo Nest features}
Echo Nest analyze API: \cite{EchoNest}.

\subsection{Cowbell Dataset}

\subsection{uspop2002}
uspop: \cite{uspop2002}.

\section{Algorithm}\label{sec:algo}

Vector quantization. Online learning.

\section{Experiments}\label{sec:experiments}

\section{Conclusion}
We are awesome. Here's how:
\begin{itemize}
\item large-scale
\item smarter shingles, based on beats and bars
\item clusters good for encoding
\item clusters good for something else?
\item free online API, code available
\end{itemize}

\small
\section{Acknowledgements}
Thierry is NSERC graduate fellow, or some title like that.

%\begin{thebibliography}{citations}
%\bibitem{Someone:04} 
%X. Someone and Y. Someone:
%{\it Title of the Book},
%Editorial Acme, Utrecht, 2004.
%\end{thebibliography}

\bibliography{tbm_bib}
